Intrusion Detection with Genetic Algorithms and Fuzzy Logic

### 2013-10-27 paper.tex
Added the trapezoidal shape to my paper.

\subsection{Fuzzy Algorithm}
In order to measure the probability that a record is an attack, a trapezoidal shape was used in the algorithm. The trapezoidal shape has four parameters: $a, b, c$, and $d$. 
\mycomment{Put in trapezoidal shape figure.} Algorithm~\ref{alg:fuzAlg} calculates the probability of a record being an attack.

@@

The four parameters a, b, c, and d are encoded into blocks of binary strings, where each block is a feature with values between 0.0 and 7.0. See Figure~\ref{fig:fuzEncodingForFeature} for an example of a block. A rule has 12 blocks of features, and at the end of the string is the type of attack.
\mycomment{Put in an example/figure of a rule.}

\begin{figure}
\centering
\caption{Fuzzy encoding for a feature}
\begin{tabular}{|c|c|c|c|} \hline
010 & 011 & 100 & 101\\
a & b & c & d\\
\hline\end{tabular}
\label{fig:fuzEncodingForFeature}
\end{figure}

>>>>

\subsection{Fuzzy Algorithm}
In order to measure the probability that a record is an attack, a trapezoidal shape was used in the algorithm. This is shown in Figure~\ref{fig:trapFigure}. The trapezoidal shape has four parameters: $a, b, c$, and $d$. Algorithm~\ref{alg:fuzAlg} calculates the probability of a record being an attack.

\begin{figure}
\centering
\psfig{file=trapFigure.jpg}
\caption{Trapezoidal shape with 4 parameters where $a\leq b\leq c\leq d$}
\label{fig:trapFigure}
\end{figure}

@@

The four parameters a, b, c, and d are encoded into blocks of binary strings, where each block is a feature with values between 0.0 and 7.0. See Figure~\ref{fig:fuzEncodingForFeature} for an example of a block. A rule has 12 blocks of features, and at the end of the string is the type of attack. An example of this is Figure~\ref{fig:rule}.

\begin{figure}
\centering
\caption{Fuzzy encoding for a feature}
\begin{tabular}{|cccc|} \hline
010 & 011 & 100 & 101\\
a=2 & b=3 & c=4 & d=5\\
\hline\end{tabular}
\label{fig:fuzEncodingForFeature}
\end{figure}

\begin{figure*}
\centering
\caption{A rule with 12 blocks of features}
\begin{tabular}{|cccc|c|cccc|c|} \hline
010 & 011 & 100 & 101   & ...... & 010 & 011 & 101 & 111   & DoS\\
a=2 & b=3 & c=4 & d=5   & ...... & a=2 & b=3 & c=5 & d=7   &\\ 
    &     & Block 1&    &        &     & Block 12& &       & Type\\
\hline\end{tabular}
\label{fig:rule}
\end{figure*}
